% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
%\usepackage{hfoldsty}
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}AKHIL P M} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document



\begin{document}

\name{\huge Akhil P M}
% \address used twice to have two lines of address
%\address{\large Naithelloor House,\\Thalachira P O,\\Kottarakara,\\Kollam\\Pin:691546\\}
\address{\large akhilpm135@gmail.com}
\address{\large (+91)9961558915}

\thispagestyle{empty} % this page does not have a header

\begin{resume}
  
  	  \section{OBJECTIVE}       
  		  To secure a promising, successful and challenging career in a reputed organization where my knowledge and skill can be effectively applied, enabling me to explore myself fully and realize my full potential.\\
  
  	  \section{EDUCATION} 
          	  {\bf Bachelor of Technology,}\hfill {\it 2009-2013}\\
          	  % \sl will be bold italic in New Century Schoolbook (or
          	  % any postscript font) and just slanted in
          	  % Computer Modern (default) font
          	  {\it University of kerala.}\\ 
          	  Institute : {\it College Of Engineering, Trivandrum,Kerala.\hfill(http://www.cet.ac.in)} \\
           	  Concentration: Computer Science \& Engineering \\ 
          	  CGPA : {\bf 7.6} \\\\
          	  {\bf Higher Secondary Education,}\hfill {\it 2008}\\        
          	  {\it Kerala State Board of Higher Secondary Education.}\\
          	  School : {\it Govt. Higher Secondary School Kokkallur,Balussery}\\
          	  Score       : {\bf 90.00\% } \\\\
          	  {\bf Secondary Education,}\hfill {\it 2006}\\
          	  {\it Kerala State Board of Secondary Education.}\\
          	  School : {\it Govt. Higher Secondary School For Boys,Koyilandy} \\ 
          	  Score       : {\bf 88.00\% } \\
	  \section{TECHNICAL \\ SKILLS} 
		  {\it Languages :} C,C++,JAVA\\-\hspace{15 mm} Python,Ruby on Rails,JavaScript{\it (preliminary knowledge)}\\
		  {\it Operating Systems Worked:} GNU/Linux, Microsoft Windows XP,Windows 7\\
		  {\it Software Packages:} Eclipse, GCC, GDB, \LaTeX.\\
	  %\section{EXPERIENCE}
		  %{\bf Software Development Engineer-Intern }\hfill {\it 2012-Summer } \\
		  %{\it Amazon.com,Chennai }

	  \section{ACADEMIC \\ PROJECTS}
	    	  {\bf Machine Parsable RESTfull web API }\hfill {\it 2013-Semester 8}\\\\
	    	  A RESTful web API is a web API implemented using {\it HTTP }and the principles of {\it REST (Representational State Transfer)}.By using  a {\it Microformats }-like grammar that helps to annotate semantics into the already existing documentation of REST services doubling them as machine-readable descriptions. Moreover, these basic annotations help to link between RESTful services in the same domain and enable automatic discovery and composition(creating {\it Mashups }) \\

                 {\bf BOINCr-Graphical Interface to manage BOINC projects}\hfill {\it 2011-Semester 5}\\\\
	     	 A graphical interface to manage a {\it BOINC project}, written in {\it Java}.\\
	     	 The {\it Berkeley Open Infrastructure for Network Computing }(BOINC) is an open source middle-ware system for volunteer and grid computing. The {\it BOINCr} provide a graphical interface to control BOINC server and to allow easy deployment of BOINC apps and work units.\\	
          \section{ACHIEVEMENTS \\ \& ACTIVITIES}
		  \begin{itemize} \itemsep -1pt
		  \item Event co-ordinator of Linux kernel API programming on Drishti-2012 annual tech fest of College of Engineering,Trivandrum.
		  \item Conducted a presentation on GREEN IT in CETEX 2010, a technical exhibition conducted by College of Engineering,Trivandrum.
		  \item Won CETAA(College of Engineering,Trivandrum Alumini Association)award for meritorious student in 2009
		  \end{itemize}
	  \section{SKILLS \& HOBBIES}
	          {\bf Languages}
	          \begin{itemize} \itemsep -2pt
	          \item English
	          \item Malayalam
		  	  \item Hindi
	          \end{itemize}
	          {\bf Personal Skills}
	          \begin{itemize} \itemsep -2pt
	          \item Disciplined, dedicated and hard working with an ability to easily adapt to changing work environment.
	          \item Keen learner with ability to learn and imbibe new knowledge.
	          \item Able to work independently/ Together in a team.
	          \end{itemize}
	          {\bf Hobbies}
	          \begin{itemize} \itemsep -2pt
	          \item Trekking
	          \item Swimming
		  	  \item Blogging
			  \item Cooking
	          \end{itemize}
	          \vspace{10 mm}                                 
          \section{PERSONAL \\ DETAILS}
	  	  \begin{tabular}{ l l }
	    	  {\bf Date of Birth:}&11 April 1991\\
	    	  %{\bf Age:} &21\\
	    	  {\bf Nationality:}&Indian\\
	    	  %{\bf Father name:}&George Kutty N A \\
	    	  % &{\it (Ex Servicemen)}\\
	    	  %{\bf Mother Name:}&L Leelamma \\
	    	  % &{\it (Teacher-Headmistress)}\\
	    	  %{\bf Marital Status:} &Single\\
	    	  {\bf Permanent Address:}& \\
	    	  &Pilakkatt Meethal House,\\
	    	  &Kuruvangad P O,\\
	    	  &Koyilandy,\\
	    	  &Calicut,\\
		  &Kerala\\
	    	  &Pin : 673305\\\\
	    	  {\bf Phone:}&Mobile : (+91)9961558915 \\
	    	  %//&Mobile: (+91)9961558915\\
	    	  {\bf Email id:} &akhilpm135@gmail.com\\
	  	  \end{tabular}
\end{resume}
\end{document}

